\chapter{Conclusion} % Main chapter title

\label{Chapter6}

This study investigated methods to enhance immersion in virtual reality experiences through the development of a wearable haptic glove. The glove is equipped with flex sensors, an IMU (MPU-6050), and a coin-type vibration motor. I utilized PWM to create vibrotactile feedback to examine participants’ ability to differentiate between various vibration cycle rates and to assess how these tactile signals influenced the perceived realism of virtual textures.

In two structured experiments, the results indicated that participants could reliably distinguish between textures based on smoothness. Higher accuracy was observed at increased cycle rates, especially when identifying differences among textures with varying levels of roughness. The subjective evaluations were rigorously analyzed using Wilcoxon Signed-Rank tests on pooled individual responses for each category, as detailed in the General Discussion. 

The findings revealed that the category of `Realistic and Aligned Tactile Sensations Felt' was significantly higher than the neutral point, confirming the system's effectiveness in delivering realistic and aligned tactile feedback. Conversely, the `Hand Ownership and Control' category was significantly lower than the neutral baseline, suggesting a diminished sense of ownership and control. In contrast, the `Immersion' category showed no statistically significant difference from the neutral point. A significant factor contributing to these results, particularly the reduced sense of hand ownership, was the suboptimal fit of the fixed-size glove, as indicated by participant feedback.

Building on these findings, future work will focus on optimizing feedback parameters, such as vibration cycle rates and duty cycles, to achieve more accurate and nuanced texture rendering. The system will also be expanded to include a wider variety of virtual textures, which will enhance realism across different surface types. Additionally, future investigations could also involve a direct comparative study of the perceptual performance of PWM-based vibrotactile feedback against other established haptic rendering techniques, such as those relying solely on frequency control or variable amplitudes. This will help us better understand their relative effectiveness and practical implications.

Furthermore, I will increase the number of participants in subsequent experiments to improve the statistical robustness and generalizability of the results. I also aim to implement adaptive feedback algorithms capable of dynamically adjusting haptic parameters based on real-time user interactions, thereby further enhancing the immersion and interactivity of VR applications.





